\documentclass[12pt,a4paper]{bsc_report}

\regno{P15/1263/2010}
\author{Eric Chomba Ng'ang'a}
\date{\today{}}
\title{Analysis of Kenyan Academic Websites using Webometric Algorithms}
\university{University of Nairobi}
\school{School of Computing and Informatics}
\supervisor{Dr. Elisha Abade}
\degree{B Sc (Computer Science)}
\submitdate{\today{}}
\submittext{Submitted in partial fulfillment of BSc (Computer Science)}


\begin{document}
\maketitle

\pagenumbering{roman}

\begin{declaration}
	The project presented in this report is my original work and has been done with the full support of my supervisor as part of the fulfillment for the Diploma of Science in Computer Science
	\\[12pt]
	Signed \dotfill Date \dotfill
	\par {$author$}
	\par {\$regno}

	\par
	This Project has been submitted as part fulfillment for the Diploma of Science in Computer Science with the approval as a Lecturer at the University of Nairobi, School of Computing and Informatics and as the Project Supervisor.
	\\[12pt]
	Signed \dotfill Date \dotfill
	\par {$supervisor$ \par}

\end{declaration}

\begin{acknowledgement}
I sincerely thank everyone who contributed to the success of this Project. I thank my supervisor {\@author}, 
for being available and resourceful. His positive contributions helped improve the project.
I also thank my colleagues in general for the useful suggestions, constructive criticisms and overall
support during the period I undertook the project.
-----Mr. Tuka-------
Thank you all.
\end{acknowledgement}

\begin{abstract}
abstract goes here
\end{abstract}

\renewcommand{\contentsname}{Table of Contents}
\tableofcontents
\clearpage %\cleardoublepage %for openright
\addcontentsline{toc}{chapter}{\listfigurename}
\listoffigures
\clearpage %\cleardoublepage %for openright
\addcontentsline{toc}{chapter}{\listtablename}
\listoftables
\clearpage %\cleardoublepage %for openright
\addcontentsline{toc}{chapter}{List of abbreviations}
\clearpage % Start a new page

\begin{abbreviations}
	API  Application Programming Interface \\
	DOS  Denial of Service \\
	DDOS Distributed Denial of Service \\
	URL  Uniform Resource Locator \\
\end{abbreviations}

\newpage

\pagenumbering{arabic}
\setcounter{page}{1}

\input{chapter_1.tex}
\input{chapter_2.tex}
\input{chapter_3.tex}
\input{chapter_4.tex}
\input{chapter_5.tex}
\input{chapter_6.tex}
\input{chapter_7.tex}
\input{references.tex}
\input{appendix.tex}

\listoftodos

\end{document}
